An upper bound to gas delivery via pressure-swing adsorption in nanoporous materials

### 2020-05-13 gas-adsorption/gas-ads-body.tex
starting on the conclusion section.

Storage of hydrogen is considerably more challenging owing to its relatively weak interaction with adsorbents. The DOE ULTIMATE deliverable capacity target~\cite{DOE} is within 6\% of the upper bound at 25$^\circ$C. Figure~\ref{fig:hydrogen-298-D} shows the theoretical upper bound curve for hydrogen storage along with a range of experimental measurements for known MOFs.  The DOE ULTIMATE deliverable capacity target is theoretically possible, however by such a small margin that we can safely rule out the possibility of reaching this target through storage and delivery of hydrogen in \emph{any} rigid substrate at room temperature. Such a material would require a void fraction of at least 94\%. On top of this, the DOE ULTIMATE target requires an optimal $|\gst|$ of 10~kJ/mol which is far greater than what is found in observed porous materials. This reflects the known fact that hydrogen interacts with substrates far more weakly than methane does. One possibility that has been pursued is storage at cryogenic temperatures. See Section~\ref{sec:cryo-hydrogen} in the Supplementary Information for the upper bound for storage of hydrogen at 77 K.

Why do we not experimentally observe materials approaching the upper bound on the deliverable capacity? Foremost, any adsorbent substrate will be composed of atoms, which will exclude the gas from some volume. Due to strong short-range interactions, substrate atoms must be uniformly distributed to achieve strong attraction for gas atoms. Uniform atom distribution sets a limit on the pore volume.
% Because strong interactions are short-range, achieving a strong attraction requires that substrate atoms be distributed throughout the volume, which places a limit on the pore volume.
In contrast, real materials have a spatially non-uniform attraction for gas atoms. The result of this is that there are regions of space with non-optimal attraction. For hydrogen, there is the further issue that there are \emph{no} known physical interactions that are sufficiently strong to give an optimal deliverable capacity at room temperature.
% Finally, real materials must have a spatially non-uniform attraction for gas atoms, resulting in some regions of space where the attraction is not optimal. For hydrogen, there is the further issue that there are \emph{no} known physical interactions that are sufficiently strong to give an optimal deliverable capacity at room temperature.

>>>>

Storage of hydrogen is considerably more challenging owing to its relatively
weak interaction with adsorbents. The DOE ULTIMATE deliverable capacity
target~\cite{DOE} is within 6\% of the upper bound at 25$^\circ$C.
Figure~\ref{fig:hydrogen-298-D} shows the theoretical upper bound curve for
hydrogen storage along with a range of experimental measurements for known
MOFs. The DOE ULTIMATE deliverable capacity target is theoretically possible,
however by such a small margin that we can safely rule out the possibility of
reaching this target through storage and delivery of hydrogen in \emph{any}
rigid substrate at room temperature. Such a material would require a void
fraction of at least 94\%. On top of this, the DOE ULTIMATE target requires an
optimal $|\gst|$ of 10~kJ/mol which is far greater than what is found in
observed porous materials. This reflects the known fact that hydrogen interacts
with substrates far more weakly than methane does. One possibility that has
been pursued is storage at cryogenic temperatures. See
Section~\ref{sec:cryo-hydrogen} in the SI for the upper bound for hydrogen
storage at 77 K.

Why do we not experimentally observe materials approaching the upper bound on
the deliverable capacity? Foremost, any adsorbent substrate will be composed of
atoms, which will exclude the gas from some volume. Due to strong short-range
interactions, substrate atoms must be uniformly distributed to achieve strong
attraction for gas atoms. Uniform atom distribution sets a limit on the pore
volume. In contrast, real materials have a spatially non-uniform attraction for
gas atoms. The result of this is that there are regions of space with
non-optimal attraction. For hydrogen, there is the further issue that there are
\emph{no} known physical interactions that are sufficiently strong to give an
optimal deliverable capacity at room temperature.
